environmental_data_preperation

### 2018-11-16 src/env_data_prep.Rmd
package updates
NAO correction :(

```{r}
naoraw <- read.csv("../data/env/amon.us.data.csv", header = FALSE) 
head(naoraw)
```

@@

And now create a raster of Gebco in aea for mapping once the SDM is done...

>>>>

```{r}
naoraw <- read.csv("../data/env/nao_pc_monthly.csv", header = FALSE) 
head(naoraw)
```

@@

And now create a raster of Gebco in aea for mapping once the SDM is done..
